These guidelines are designed to help students present their work clearly and professionally, enabling graders to provide accurate and timely feedback. With over a hundred assignments to review, a consistent format and organized presentation allow graders to focus on evaluating each solution rather than adjusting to different styles. By following these standards, students support a smoother grading process that benefits everyone, making it easier to receive prompt and meaningful feedback.

\section*{Code Submission Guidelines}
\begin{enumerate}[label=\arabic*.]
    \item Ensure code is properly indented, with comments explaining the purpose and logic of each section.
    \item Follow the naming convention specified in each template, noted at the top of the code.
    \item Every programming-related files including the dataset must be compressed as a single zip-file. 
\end{enumerate}

\section*{Typed Assignment Guidelines (Preferred)}
\begin{enumerate}[label=\arabic*.]
    \item Clearly label each section and problem with appropriate headings and subheadings.
    \item Use LaTeX or a built-in equation editor for all mathematical expressions to maintain clarity.
    \item Submit typed assignments in PDF format to prevent formatting issues (Word documents are not accepted).
    \item This pdf file must not be include in the programming zip file. 
    \item Embed any required diagrams or plots, with clear captions or labels.
    \item Choose legible fonts in terms of size, style, and color.
    \item Start a new page for each problem to enhance clarity and organization.
\end{enumerate}

\section*{Hand-Written Assignment Guidelines}
\begin{enumerate}[label=\arabic*.]
    \item If any part of the handwriting is deemed illegible, that section will not be graded.
    \item Only black or blue ink pens are allowed; HB pencils are not permitted.
    \item Assignments must be neatly organized, with clear headings, subheadings, and numbered sections.
    \item Text should flow from left to right and top to bottom on each page.
    \item Use standard 8.5"x11" lined or grid paper only.
    \item Maintain at least a 1-inch margin on all sides of each page.
    \item Begin a new page for each problem.
    \item Number pages visibly at the bottom to avoid misordering.
    \item Include your name on the first page of the assignment.
    \item All page must be converted to a single pdf file. 
\end{enumerate}

\section*{Note}
Failure to comply will result in a mark deduction for each violation.
